%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
% Modified by:
% Alexander Reaves (http://www.alexanderreaves.me/)
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style
\usepackage{hyperref}
\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\usepackage{enumitem}%http://ctan.org/pkg/enumitem
\usepackage{amsmath}
\usepackage{fontawesome}
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
% Your name
%\usepackage{color}
%\hypersetup{colorlinks=true, urlcolor = blue, linkcolor = black}


\name{Alexander Michael Reaves} 

% Your address
\address{\faEnvelope
\href{mailto:amr200@cam.ac.uk}{ amr200@cam.ac.uk}
$\mid$ \faLinkedinSquare
 \href{https://www.linkedin.com/in/alexander-reaves/}{ {alexander-reaves}} $\mid$ \faPhone \href{tel:+14802131323}{ +1 (480)  213 -- 1323}   } 


\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

     %I am an American student at Yale-NUS College, a partnership college between Yale University and the National University of Singapore. I have a broad range of physics and engineering related research experiences and am currently interested in developing of carbon-neutral infrastructure.

%%%focus more on experience and add future research interests

\begin{rSection}{Education}

{\bf \large  University of Cambridge} \hfill {Cambridge, UK}\\
{\em Masters of Research in Future Propulsion and Power} \hfill { October 2021 {\textendash}  August 2022 }


{\bf \large  Yale-NUS College} \hfill { Singapore}\\
{\em Bachelor of Science in Physical Sciences (Physics)} \hfill { August 2017 {\textendash}  May 2021 }

{\bf \large  University of Cambridge, Pembroke College}\hfill{Cambridge, UK}\\
{\em Coursework in Mathematics and Theoretical Physics}\hfill{May 2019 {\textendash}   June 2020}


{\bf \large  Phoenix Country Day School} \hfill { Arizona, USA}\\
{\em High School Diploma} \hfill { August 2014 {\textendash}  June 2017}

{\bf \large  Arizona State University} \hfill { Arizona, USA}\\
{\em Coursework in Computer Science} \hfill { May {\textendash} July 2016}



\end{rSection}
%----------------------------------------------------------------------------------------


%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{RESEARCH EXPERIENCE}
%\begin{rSubsection}{Yale-NUS Physical Sciences Department and University of Cambridge}{} {Senior Capstone Project} 
%{August 2020 {\textendash} Present}
%\item  Explored the feasibility of sand-powered energy generation
%\item 

%\end{rSubsection}
\begin{rSubsection}{Yale-NUS Physical Sciences Major}{Yale-NUS College \& University of Cambridge}{Capstone Student}{August 2020 {\textendash} May 2021}
\item Conducted a yearlong research project modeling the interactions between granular flows and hydropower turbines. 
\item Met weekly with supervisors from the University of Cambridge and Yale-NUS College to present relevant findings. 
%\item Wrote a thesis capturing the results of capstone research project. 

\end{rSubsection}


\begin{rSubsection}{NASA Ames Research Center}{National Aeronautics and Space Administration} {Summer Intern} 
{June  {\textendash} August 2020}
\item  Used Creo Parametric to design 3D models of components for the International Space Station.
\item 3D printed and tested multiple iterations of a $\text{CO}_2$ sensor which could be manufactured in space.

\end{rSubsection}

\begin{rSubsection}{Yale-NUS Sciences Department}{Yale-NUS College}{Summer Research Assistant}{  June  {\textendash} August 2019}
\item Awarded full funding from the JY Pillay Global-Asia Programme to work under Prof. Chelsea Sharon to research the feasibility of radio astronomy data collection in Singapore. 
\item  Designed and built a radio telescope which will be used to test the suitability of  Singapore's RF environment for radio astronomy observations.
\item Programmed basic data-collection and signal processing interfaces for the telescope.

\end{rSubsection}

\begin{rSubsection}{Centre for Advanced 2D Materials}{National University of Singapore}{Research Assistant}{May 2018 {\textendash} August 2019}
\item Awarded full funding from JY Pillay Global-Asia Programme to work under Prof. Shaffique Adam to research superconductivity in twisted bilayer graphene.
\item Created and ran simulations to determine the electronic band properties and lattice structure of superconductive twisted bilayer graphene.
\item Presented relevant papers and research findings in group meetings and weekly journal clubs.
\item Published results of research in \textit{Solid State Communications}. To date, the paper has been cited over 50 times. 
\end{rSubsection}

\newpage
%----------------------------------------------

\begin{rSubsection}{Center for Embedded Systems }{Arizona State University}{Summer Intern}{\normalfont{May {\textendash} July 2016}}
\item Developed methodologies for optimizing wireless connections on embedded computer systems.
\item Wrote wireless transmission code on an arduino in order to support a graduate student on his wireless pH sensor project.
\end{rSubsection}


%\begin{rSubsection}{ASU NEWSPACE}{Arizona State University}{Intern for Program Manager Scott Smas	}{	\normalfont{  May 2016 {\textendash} July 2016}}
%\item 	Researched commercial aerospace enterprises that would be interested in joining ASU NewSpace's MILO Institute initiative.
%\item Managed the transfer of ASU NewSpace's calendaring system from a pen-and-paper system to a cloud-accessible Google Calendar.

%\end{rSubsection}






\end{rSection}



\begin{rSection}{OTHER PROFESSIONAL EXPERIENCE }

%------------------------------------------------
\begin{rSubsection} {Open Ventilator System Initiative (OVSI)}{University of Cambridge}
 {Engineer / Engineering Coordinator }{March 2020 {\textendash} June 2020}
\item  Assisted in the design and creation of multiple versions of an affordable, hospital-quality, ventilator system that can be sustainably manufactured and maintained in low and middle-income countries.
\item Managed information sharing and co-development between engineering groups in the United Kingdom, Kenya, Uganda, and Ethiopia.
\end{rSubsection}

\begin{rSubsection}
{United Nations Office for Outer Space Affairs}{United Nations}{Online Volunteer}{	 December 2018 {\textendash} March 2019}

 \item Researched various methodologies for wastewater recycling and their potential to be applied in order to help achieve UN Sustainable Development Goal 6: Sustainable Management of Water and Sanitation for All.
\item  Wrote articles for the UN's Space4Water portal which explain the potential applications of space technologies for water management to a non-technical audience.

\end{rSubsection}

%\begin{rSubsection}{NOBLE MISSION FOR CHANGE INITIATIVE}{ Abuja, Nigeria}{United Nations Online Volunteer}{	\normalfont{  November 2018 {\textendash} January 2019}}
%\item  Created informative data visualizations which assist the Noble Mission for Change Initiative in its mission to improve access to quality education in Africa.
%\end{rSubsection}

%\begin{rSubsection}{SAGA COLLEGE, YALE-NUS COLLEGE }{Singapore}{Student Associate	}{  \normalfont{  2017 {\textendash} 2018}}
%\item Conceptualized and implemented community-building events ranging from monthly birthday parties to informal academic talks for a residential college community of over 800 undergraduates and faculty members.
%\item Oversaw the day-to-day logistics of office procedures, such as mail distribution and inventory management.
%\end{rSubsection}

\end{rSection}


%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{PUBLICATIONS AND PRESENTATIONS} 
\begin{itemize}[leftmargin={0 pt}, label={}, topsep=0pt]

\item \href{https://doi.org/10.1016/j.ssc.2018.07.013}{\textbf{Singlet superconductivity enhanced by charge order in nested twisted bilayer graphene Fermi surfaces}  
Evan Laksono, Jia Ning Leaw, \textbf{Alexander Reaves}, Manraaj Singh, Xinyun Wang, Shaffique Adam, Xingyu Gu;
Solid State Communications,
Volume 282,
Pages 38-44,
October 2018\\
https://doi.org/10.1016/j.ssc.2018.07.013 }

\item \href{https://www.space4water.org/news/wastewater-recycling-iss-and-singapore}{\textbf{Wastewater recycling on the ISS and in Singapore} \\
\textbf{Alexander Reaves}; United Nations Office of Outer Space Affairs, Space4Water, February 2019\\ https://www.space4water.org/news/wastewater-recycling-iss-and-singapore}

\item \href{http://meetings.aps.org/Meeting/MAR19/Session/S14.10}{\textbf{Magnetotransport properties in twisted bilayer graphene at magic angle} \\
Evan Laksono,  \textbf{Alexander Reaves}, Manraaj Singh, Xingyu Gu, Jia Ning Leaw, Nimisha Raghuvanshi, Shaffique Adam; American Physical Society, Abstract: S14.00010, March 2019\\ http://meetings.aps.org/Meeting/MAR19/Session/S14.10}

\end{itemize}
\end{rSection}
%----------------------------------------------------------------------------------------
\begin{rSection}{HONORS AND AWARDS}

\begin{rSubsection}
{President's Special Award for Pandemic Service}{2020}{}{}
\item Award given to OVSI from the Royal Academy of Engineering for contributions to addressing the challenges of the COVID-19 pandemic. 
\end{rSubsection}


\begin{rSubsection}
{JY Pillay Global-Asia Programme Research Award}{2018 \& 2019}{}{}
\item Received full funding  to construct a radio telescope to test the suitability of  Singapore's RF environment for radio astronomy observations during summer 2019.
    \item Received full funding to research superconductivity in twisted bilayer graphene during summer 2018.
\end{rSubsection}


%\textbf{JY Pillay Global-Asia Programme Research Award}\hfill 2018\\


% \\ \itab{Process Control (ongoing)} \tab{} \tab{Electrodynamics}

\end{rSection}




\newpage
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Technical Strengths}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Computer Languages &  C, C++, MATLAB, Python, R \\
Software \& Tools &  Creo, LabVIEW, \LaTeX, Mathematica, Microsoft Office 
%\\ Operating Systems & MacOS, Windows, Ubuntu
\end{tabular}

\end{rSection}
%----------------------------------------------------------------------------------------
\begin{rSection}{Extra Curricular}
\textbf{Yale-NUS College Student Government (Director of Academics)} \hfill May 2020 {\textendash}  May 2021
\textbf{Yale-NUS Science Society (President)} \hfill  January 2018 {\textendash}  May 2019 \\
\textbf{Yale-NUS Sexual Assault Prevention and Education Taskforce} \hfill January 2018 {\textendash}  May 2018 
\end{rSection}



\begin{rSection}{References}


\textbf{James Taylor} $|$ 
Assistant Professor, Department of Engineering $|$
University of Cambridge\\
1 JJ Thomson Ave, Cambridge, United Kingdom, CB3 0DY\\
jvt24@cam.ac.uk $|$ 
+44 7950-852578

\textbf{Sam Grimshaw} $|$ 
Mitsubishi Heavy Industries Senior Research Fellow $|$
University of Cambridge\\
1 JJ Thomson Ave, Cambridge, United Kingdom, CB3 0DY\\
sdg33@cam.ac.uk $|$ 
+44 1223-337581


\textbf{Chelsea Electra Sharon} $|$
Assistant Professor, Physical Sciences $|$
Yale-NUS College\\
01-101, 10 College Avenue West, Singapore, 138609\\
chelsea.sharon@yale-nus.edu.sg $|$
+65 6601-7558


\textbf{Zhuang Bilin} $|$
Assistant Professor, Physical Sciences $|$
Yale-NUS College\\
01-101, 10 College Avenue West, Singapore, 138609\\
zhuang.bilin@yale-nus.edu.sg $|$
+65 6419-1275



\end{rSection}





\let\thefootnote\relax\footnotetext{Last Updated: \today}

\end{document}
